%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.7\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{COLOR_1}{\href{https://www.linkedin.com/in/marcin-kruk-a5486111a/}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Marcin Kruk}}}}}} % First name
	
	\vspace{10pt}
	
	{\huge Physicist who does software} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Phone}{12}{+48 694 750 175}\\
	\icon{Envelope}{12}{\href{mailto:marcin0kruk@gmail.com}{marcin0kruk@gmail.com}}\\
	\icon{Github}{12}{\href{https://github.com/marcinkruk}{github.com/marcinkruk}}\\
\end{minipage}

\vspace{0.5cm}

\cvsect{About}

 %   \begin{center}
 %   \begin{minipage}[t]{0.75\textwidth}
 %   \begin{center}
%    \textit{
    I'm a physicist with over 5 years of software development experience. After a~professional excursion into computer security and space business, I'm seeking a~career opportunity where I could use my software development skills in~conjunction with my education as a~physicist.
%    }
%    \end{center}
%    \end{minipage}
%    \end{center}

\cvsect{Experience}
\begin{entrylist}
	\entry
		{2017 -- now}
		{\href{https://astripolska.pl/}{Astri Polska}}
		{Software Developer}
        {\underline{Technical responsibilites}:\\
        Software development in C++, Java and Rust. Setup of continuous integration infrastructure in Jenkins and Gitlab-CI. Deployment and integration of many component VM environment. Basic Linux administration.\\
        \underline{Projects}:\\
        ARTSi -- an asynchronous real-time simulator written in Rust.\\
        Accepto -- next generation system for satellite ground control.\\
        THEOS-2 -- development and integration of a satellite model.\\
        Neosat, Metop -- rack cabinets for validation of satellite platforms.\\
        Those projects were realized in coordination with Airbus D\&S and European Space Agency.\\
        \underline{Other}:\\
        I took the role of Technical Lead for Accepto project. I was responsible for technical decisions in the project and I coordinated our work with the client.\\
        I was involved in several projects proposals, providing technical input to the documents.
        \\ \texttt{C++}\slashsep\texttt{Java}\slashsep\texttt{SpringBoot}\slashsep\texttt{Gitlab-CI}\slashsep\texttt{Docker}\slashsep\texttt{Rust}\slashsep\texttt{Linux}}
	\entry
		{2016}
		{\href{https://fudosecurity.com/}{Fudo Security}}
		{Junior Software Developer}
	    {Software development of their flagship product Fudo PAM.\\
		\texttt{C}\slashsep\texttt{FreeBSD}\slashsep\texttt{Postgres}}
\end{entrylist}

\cvsect{Skills}

\begin{minipage}[t]{0.3\textwidth}
\vspace{-\baselineskip}
\begin{barchart}{2.5}
	\baritem{C++}{100}
	\baritem{GNU/Linux}{90}
	\baritem{Rust}{30}
\end{barchart}
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
\vspace{-\baselineskip}
\begin{barchart}{2.5}
	\baritem{Java}{90}
	\baritem{SpringBoot}{50}
	\baritem{Python}{20}
\end{barchart}
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
\vspace{-\baselineskip}
\begin{barchart}{2.5}
	\baritem{Git and CI}{70}
	\baritem{Docker}{40}
	\baritem{Databases}{15}
\end{barchart}
\end{minipage}

\cvsect{Education}

\begin{entrylist}
	\entry
		{2014 -- 2021}
		{\href{https://www.fuw.edu.pl/}{Physics, University of Warsaw}}
		{Master's degree}
		{Specialization: Mathematical and computer modelling of physical phenomena.\\
		\href{https://github.com/marcinkruk/mgr/blob/master/mkruk-thesis-20210915.pdf}{Thesis: Multiscale nonlinear Granger causality in currency exchange markets.}}
	\entry
		{2011 -- 2014}
		{\href{https://www.fuw.edu.pl/}{Nanostructures engineering, University of Warsaw}}
		{Bachelor's degree}
		{A combined physics and chemistry course.\\
		\href{https://github.com/marcinkruk/mgr/blob/master/lic/mkruk-lic.pdf}{Thesis: Long-range asymptotic behaviour of molecular hydrogen wavefunction.}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.23\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Polish} -- native\\
	\textbf{English} -- proficient\\
	\textbf{German} -- basic
\end{minipage}
\begin{minipage}[t]{0.75\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Interests}
	
	\textbf{\href{https://www.facebook.com/AKSZlyKosmodysk}{Ultimate Frisbee}} -- I play on competitive european level and manage the team.\\
	\textbf{Sailing} -- I used to teach sailing on summer youth camps.
\end{minipage}
\hfill

%\vspace{\fill}
%\footnotesize{Wyrażam zgodę na przetwarzanie moich danych osobowych dla potrzeb niezbędnych do realizacji procesu tej oraz przyszłych rekrutacji (zgodnie z ustawą z dnia 10 maja 2018 roku o ochronie danych osobowych (Dz. Ustaw z 2018, poz. 1000) oraz zgodnie z Rozporządzeniem Parlamentu Europejskiego i Rady (UE) 2016/679 z dnia 27 kwietnia 2016 r. w sprawie ochrony osób fizycznych w związku z przetwarzaniem danych osobowych i w sprawie swobodnego przepływu takich danych oraz uchylenia dyrektywy 95/46/WE (RODO)).}
%----------------------------------------------------------------------------------------

\end{document}
